|

### 2025-02-25 docs/paper.qmd
Small fixes

[^1]: The terms "reproduction" and "replication" are at times used as synonyms but have different meanings. Reproduction refers to achieving the same results of a prior study using the same materials (code, procedures, and data), while replication refers to duplicating the results of a of a prior study using the same code and procedures but new data [@NSF_2015; @BCKU_2024]. For a more in-depth discussion of the differences and related terminological debate, see @DJ_2024.

>>>>

[^1]: [We received institutional approval for this study.]{.content-visible when-meta="anonymize"} The terms "reproduction" and "replication" are at times used as synonyms but have different meanings. Reproduction refers to achieving the same results of a prior study using the same materials (code, procedures, and data), while replication refers to duplicating the results of a of a prior study using the same code and procedures but new data [@NSF_2015; @BCKU_2024]. For a more in-depth discussion of the differences and related terminological debate, see @DJ_2024.

### 2025-02-25 docs/presentation.qmd
Small fixes

center_table <- function(x) {
	x[1] <- paste0("\\begin{center}", x[1], "\\end{center}")
	x
}
```

@@

```{r}

# Later quotes need checking still - lots of potentially interesting stuff
quotes <-c(11, 16, 18, 66, 67, 72, 80, 82, 84)
# 83, 87, 88, 91, 105, 110
 sd %>%
 	filter(row_number() %in% quotes) %>%
 	transmute(
 		Condition = sprintf(
 			"%s/%s", ifelse(exp_tment_collab, "Collab", "Control"),
 			ifelse(exp_tment_private, "Private", "Public")
 		),
 		Quote = exp_reflect
 	) %>% kable(booktabs = TRUE, linesep = "") %>% 
 	kable_styling(full_width = TRUE, font_size = 7)  %>% 
 	column_spec(1, width = "1.5cm")

>>>>

center_table <- function(x) {
	x[1] <- paste0("\\begin{center}", x[1], "\\end{center}")
	x
}

script_size <- function(x) {
	x[1] <- paste0("\\scriptsize", x[1], "\\normalsize")
	x
}

tiny_size <- function(x) {
	x[1] <- paste0("\\tiny", x[1], "\\normalsize")
	x
}
```

@@

```{r, asis = TRUE}

quotes <-c(11, 16, 18, 66, 67, 72, 80, 82, 84)
df <- sd %>%
 	filter(row_number() %in% quotes) %>%
 	transmute(
 		Condition = sprintf(
 			"%s/%s", ifelse(exp_tment_collab, "Collab", "Control"),
 			ifelse(exp_tment_private, "Private", "Public")
 		),
 		Quote = exp_reflect
 	)

gt(df) %>% 
	cols_width(
		`Condition` ~ pct(15),
		`Quote` ~ pct(85)
	) %>%
	tab_options(table.font.size = 7) %>%
	as_latex() %>%
	tiny_size()
```
